Numerical investigation of viscous flow instabilities through heterogeneous porous media. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
change group name

\medskip
As mentioned in Section \ref{section:ViscousInstabilities}, \textit{viscous fingering} is characterized by the formation of flow patterns, called viscous fingers. The geometrical evolution of these patterns provides good indications on capturing and tracking any instabilities in the flow front. Figure \ref{fig:3DChannel_PermMesh} shows the initial permeability distribution for the simulations described in this section. The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$. No-slip conditions are applied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain. Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0) = 0.80$, which was displaced by a pure (wetting) fluid. The domain was designed to capture preferential flow pathways, as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.

>>>>

As mentioned in Section \ref{section:ViscousInstabilities}, viscous instabilities is characterised by the formation of flow patterns, called viscous fingers. The geometrical evolution of these patterns provides good indications on capturing and tracking any instabilities in the flow front. Figure \ref{fig:3DChannel_PermMesh} shows the initial permeability distribution for the simulations described in this section. The surface on the left hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$. No-slip conditions are applied everywhere else (\ie no flux across the boundaries) except at the right hand side of the domain where the fluid is allowed to leave the domain. Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0) = 0.80$, which was displaced by a pure (wetting) fluid. The domain was designed to capture preferential flow pathways, as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.
